---
title: "Combining interest"
author: "Pearl Muensterman"
date: "12/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(olsrr)
library(MASS)
```

```{r}
data3 <- read_excel("clean_amusement_data.xlsx")

str(data3)
data3 <- mutate(data3, main = if_else(main == "No", 0, 1))
data3 <- mutate(data3, story = if_else(story == "No", 0, 1))
data3 <- mutate(data3, Indoor = if_else(location == "Indoor", 1, 0),
                     Outdoor = if_else(location == "Outdoor", 1, 0))
data3 <- mutate(data3, interest_adult_avg = (interest_adult + interest_teen + interest_ya)/3)
data_com <- filter(data3, vehicle != "Show")
data_com <- dplyr::select(data_com, -location, -name, -vehicle, -interest_adult, -interest_teen, -interest_ya)
```


All Possible
```{r}
park_model <- lm(wait ~ ., data = data_com)
all_poss_model_3 <- ols_step_all_possible(park_model)
which.max(all_poss_model_3$adjr)
all_poss_model_3[5812,]$adjr
all_poss_model_3[5812,]$predictors
which.min(all_poss_model_3$cp)
all_poss_model_3[92,]$predictors
```
adjusted r^2: wait ~ main + age + length + story + sense + Indoor + Outdoor + interest_adult_avg 
adjusted r^2 = 0.4970444 
cp: wait ~ length + Outdoor + interest_adult_avg 

```{r}
full_mod <- lm(wait ~ ., data = data_com)
base_mod <- lm(wait ~ 1, data = data_com)
forward_mod <- stepAIC(base_mod, direction = "forward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
forward_mod$anova
```
Outdoor, interest_adult_avg, length, story, Indoor


```{r}
backward_mod <- stepAIC(full_mod, direction = "backward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
backward_mod$anova
```
length, story, Indoor, Outdoor, interest_adult_avg

```{r}
step_mod <- stepAIC(full_mod, direction = "both", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
step_mod$anova
```
length, story, Indoor, Outdoor, interest_adult_avg


```{r}
mod3 <- lm(wait ~ length + story + Indoor + Outdoor + interest_adult_avg, data = data_com)
summary(mod3)
```
Adj r2 0.4928 (best so far)


```{r}
mod3_sig <- lm(wait ~ length + Outdoor + interest_adult_avg, data = data_com)
summary(mod3_sig)
```
adj r2 0.4832

```{r}
residuals_show <- rstandard(mod3)
qqnorm(residuals_show)
qqline(residuals_show)
```
Upper tail could use some help. Other than that its good. page 138 says positive skewed EVEN W/O SHOWS

```{r}
fitted_show <- fitted.values(mod3)
ggplot()+
  geom_point(aes(x = fitted_show, y = residuals_show))
```
