---
title: "Frozen In Line: An Analysis of Amusement Park Wait Times"
author: "Amy Bertelsman, Pearl Muensterman, & Ethan Morlock"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readxl)
library(olsrr)
library(MASS)
```

## Introduction 
- Model wait time for amusement park attractions
- Why important?
  + Park managers
  + Park visitors
- Hypotheses about longer wait times
  + Attraction length
  + Higher interest
  + Main attractions
  + New attractions
  + Roller coasters
  + Outdoor attractions

## Data 
- Collected for a senior thesis 
- Collected in 2018 
- Three Amusement Parks 
  + Disney World 
  + Disneyland 
  + Universal Studios (Orlando) 
- 128 observations
- 17 variables 

## Variables 
:::::::::::::: {.columns}
::: {.column}
- Attraction Name
- **Main Ticket Attraction** 
- Attraction Age 
- Attraction Length 
- Height Requirement 
- Interest Level of Preschool
- Interest Level of Grade School 
- Interest Level of Teens
- Interest Level of Young Adults 
:::
::: {.column}
- Interest Level of Adults
- Interest Level of Seniors 
- Attraction Vehicle Type 
- Average Wait Time (response)
- **Based on Popular Story**
- **Attraction Environment** 
- Average Thrill Level 
- Average Sensory Level 
:::
::::::::::::::

## Model One - All Attractions  
- Compared results of variable selection methods
  + Forward selection
  + Backward elimination
  + Step-wise regression
  + All-possible regression
- Best model from all-possible regression
  + Length, teen interest, young adult interest, senior interest, thrill level, based on story, outdoor
- Adjusted R-squared: 0.4633

## Model Two - No Shows 
- Decided to get rid of shows
  + Influential points, outliers
- Rides and shows length difference 
- Best Model
  + Main attraction, age, length, teen interest, young adult interest, senior interest, based on story, sense level, indoor, outdoor
- Adjusted R-Squared: 0.4923

## Model Three - Aggregating Interest Level 
- Noticed three variables were similar
  + Collinearity
- Created a variable average adult interest
  + Combined teen interest, young adult interest, adult interest
- Best Model
  + Main attraction, age, length, based on story, sense level, indoor, outdoor, average adult interest
- Adjusted R-Squared = 0.4970

## Model Four - Ride vs Show 
- Returned shows 
- Differentiating between rides and shows 
  + Used vehicle to create an indicator variable for ride (1) and show (0) 
- Best Model
  + Length, preschooler interest, based on story, thrill  level, outdoor, average adult interest, ride 
- Adjusted R-squared: 0.6141 
- Best overall model
- Investigated possibility of transformation


## Conclusion 
- Less than stellar results
- Need more relevant variables to determine wait time
  + Location in park (ride groupings)
  + Number of people serviced in an hour
  + Daily records of number of people in park for a year
  + Time and money spent on advertising (in general or specific ride)
  + Cost of each ride, if applicable
- Residual analysis shows evidence of nonlinear relationship


## Appendix 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
data <- read_excel("clean_amusement_data.xlsx")
ggplot(data) +
  geom_histogram(aes(x= length)) + 
  ggtitle("Distribution of Length of Attraction") + 
  xlab("Length of Attraction") +
  ylab("Count")
```


## Appendix 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
data2 <- read_excel("clean_amusement_data.xlsx")
data2 <- mutate(data2, main = if_else(main == "No", 0, 1))
data2 <- mutate(data2, story = if_else(story == "No", 0, 1))
data2 <- mutate(data2, Indoor = if_else(location == "Indoor", 1, 0),
                     Outdoor = if_else(location == "Outdoor", 1, 0))
data_no_show <- filter(data2, vehicle != "Show")
data_no_show <- dplyr::select(data_no_show, -location, -name, -vehicle)

ggplot(data_no_show) +
  geom_histogram(aes(x = length))+ 
  ggtitle("Distribution of Length of Ride") + 
  xlab("Length of Ride") +
  ylab("Count")
```

## Appendix
```{r, echo = FALSE, warning = FALSE}
data4 <- read_excel("clean_amusement_data.xlsx")
data4 <- mutate(data4, main = if_else(main == "No", 0, 1))
data4 <- mutate(data4, story = if_else(story == "No", 0, 1))
data4 <- mutate(data4, Indoor = if_else(location == "Indoor", 1, 0),
                     Outdoor = if_else(location == "Outdoor", 1, 0))
data4 <- mutate(data4, interest_adult_avg = (interest_adult + interest_teen + interest_ya)/3)
data4 <- mutate(data4, ride = if_else(vehicle == "Show", 0, 1))
data_ride <- dplyr::select(data4, -location, -name, -vehicle, -interest_adult, -interest_teen, -interest_ya)
best_mod <- lm(wait~length + interest_preschool + story + thrill + Outdoor + interest_adult_avg + ride, data = data_ride)
residuals_ride <- rstandard(best_mod)
qqnorm(residuals_ride)
qqline(residuals_ride)
```

## Appendix 
```{r, echo = FALSE, warning = FALSE}
fitted_ride <- fitted.values(best_mod)
ggplot()+
  geom_point(aes(x = fitted_ride, y = residuals_ride)) +
  ggtitle("Residuals vs Fitted Values Plot") + 
  xlab("Fitted Values") +
  ylab("Residuals")
```

## Appendix 
```{r, echo = FALSE, warning = FALSE}
mod_wo_preschool <- lm(wait~ length + story + thrill + Outdoor + interest_adult_avg + ride, data = data_ride)
mod_w_preschool_pred <- lm(interest_preschool ~ length + story + thrill + Outdoor + interest_adult_avg + ride, data = data_ride)
ggplot()+
  geom_point(aes(x = mod_w_preschool_pred$residuals, y = mod_wo_preschool$residuals))+
  ggtitle("Partial Regression Plot for Preschooler Interest Level") + 
  xlab("Residuals of Model Regressed on Preschoolers") +
  ylab("Residuals of Model without Preschoolers")
```

## Appendix 
```{r, echo = FALSE, warning = FALSE}
mod_wo_length <- lm(wait~ interest_preschool + story + thrill + Outdoor + interest_adult_avg + ride, data = data_ride)
mod_w_length_pred <- lm(length ~ interest_preschool + story + thrill + Outdoor + interest_adult_avg + ride, data = data_ride)
ggplot()+
  geom_point(aes(x = mod_w_length_pred$residuals, y = mod_wo_length$residuals))+
  ggtitle("Partial Regression Plot for Length of Attraction") + 
  xlab("Residuals of Model Regressed on Length") +
  ylab("Residuals of Model without Length")
```

## Appendix 
```{r, echo = FALSE, warning = FALSE}
mod_wo_thrill <- lm(wait~ length + story + interest_preschool + Outdoor + interest_adult_avg + ride, data = data_ride)
mod_w_thrill_pred <- lm(thrill ~ length + story + interest_preschool + Outdoor + interest_adult_avg + ride, data = data_ride)
ggplot()+
  geom_point(aes(x = mod_w_thrill_pred$residuals, y = mod_wo_thrill$residuals))+
  ggtitle("Partial Regression Plot for Average Thrill Level") + 
  xlab("Residuals of Model Regressed on Thrill") +
  ylab("Residuals of Model without Thrill")
```

## Appendix 
```{r, echo = FALSE, warning = FALSE}
mod_wo_adult <- lm(wait~ length + story + interest_preschool + Outdoor + thrill + ride, data = data_ride)
mod_w_adult_pred <- lm(interest_adult_avg ~ length + story + interest_preschool + Outdoor + thrill + ride, data = data_ride)
ggplot()+
  geom_point(aes(x = mod_w_adult_pred$residuals, y = mod_wo_adult$residuals))+
  ggtitle("Partial Regression Plot for Average Adult Interest") + 
  xlab("Residuals of Model Regressed on Average Adults") +
  ylab("Residuals of Model without Average Adults")
```

