---
title: "Project_EDA"
author: "Da Crew feat 3/4 of Infectious Diseasez"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(olsrr)
library(MASS)
```

```{r}
data <- read_excel("clean_amusement_data.xlsx")
str(data)
data <- mutate(data, main = if_else(main == "No", 0, 1))
data <- mutate(data, story = if_else(story == "No", 0, 1))
data <- mutate(data, Indoor = if_else(location == "Indoor", 1, 0),
                     Outdoor = if_else(location == "Outdoor", 1, 0))
data <- dplyr::select(data, -location, -name, -vehicle)
```
0 = not main, 1 = main; same for story
Location column removed, indoor and outdoor columns made. 
If 0 in both indoor and outdoor columns than the ride is both indoor and outdoor

Very longgggg
```{r}
park_model <- lm(wait ~ ., data = data)
all_poss_model <- ols_step_all_possible(park_model)
```

```{r}
full_mod <- lm(wait ~ ., data = data)
base_mod <- lm(wait ~ 1, data = data)
forward_mod <- stepAIC(base_mod, direction = "forward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
forward_mod$anova
```
Length, interest_ya, Outdoor, story, interest_senior selected from forward selection.

```{r}
backward_mod <- stepAIC(full_mod, direction = "backward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
backward_mod$anova
```
Length, interest_teen, interest_ya, story, thrill, outdoor are all selected from backward

Four are common between the two approaches.

```{r}
step_mod <- stepAIC(full_mod, direction = "both", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
step_mod$anova
```
Same variables as backward selection

