---
title: "Project_EDA"
author: "Da Crew feat 3/4 of Infectious Diseasez"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(olsrr)
library(MASS)
```

```{r}
data <- read_excel("clean_amusement_data.xlsx")
count_shows <- data[which(data$vehicle == "Show"),]
ggplot(data = count_shows) +
  geom_point(aes(x = length, y = wait))
ggplot(data = data) +
  geom_point(aes(x = length, y = wait))

str(data)
data <- mutate(data, main = if_else(main == "No", 0, 1))
data <- mutate(data, story = if_else(story == "No", 0, 1))
data <- mutate(data, Indoor = if_else(location == "Indoor", 1, 0),
                     Outdoor = if_else(location == "Outdoor", 1, 0))
data <- dplyr::select(data, -location, -name, -vehicle)

ggplot(data) +
  geom_histogram(aes(x= length))
```
Interest_teen and interest_ya are very similar in ratings, possible collinearity
0 = not main, 1 = main; same for story
Location column removed, indoor and outdoor columns made. 
If 0 in both indoor and outdoor columns than the ride is both indoor and outdoor


```{r}
park_model <- lm(wait ~ ., data = data)
all_poss_model <- ols_step_all_possible(park_model)
which.max(all_poss_model$adjr)
all_poss_model[9949,]$adjr
all_poss_model[9949,]$predictors
which.min(all_poss_model$cp)
all_poss_model[1941,]$predictors
```
Adjusted R^2 has length, interest_teen, interest_ya, interest_senior, story, thrill, and Outdoor
Cp gives length, interest_ya, interest_senior, story, and Outdoor


```{r}
full_mod <- lm(wait ~ ., data = data)
base_mod <- lm(wait ~ 1, data = data)
forward_mod <- stepAIC(base_mod, direction = "forward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
forward_mod$anova
```
Length, interest_ya, Outdoor, story, interest_senior selected from forward selection.

```{r}
backward_mod <- stepAIC(full_mod, direction = "backward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
backward_mod$anova
```
Length, interest_teen, interest_ya, story, thrill, outdoor are all selected from backward

Four are common between the two approaches.

```{r}
step_mod <- stepAIC(full_mod, direction = "both", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
step_mod$anova
```
Same variables as backward selection

```{r}
forward_model <- lm(wait ~ length + interest_ya + Outdoor + story + interest_senior, data = data)
summary(forward_model)
anova(forward_model)
```
Says interest_senior is not significant

```{r}
backward_step_model <- lm(wait ~ length + interest_teen + interest_ya + story + thrill + Outdoor, data = data)
summary(backward_step_model)
anova(backward_step_model)
```
Summary says interest_teen and interest_ya and thrill are not significant
ANOVA says all are signficant

Highest adjusted R^2 from all possible model:
```{r}
rsq_model <- lm(wait ~ length + interest_teen + interest_ya + interest_senior + thrill + story + Outdoor, data = data)
summary(rsq_model)
anova(rsq_model)
```
Interest_senior, interest_ya, and interest_teen and thrill not significant in summary
Thrill not significant in anova
Best model based on adjusted R-squared value (0.4633) (relationship with R^2 in all possible model? bc same as above)

Lowest Cp from all possible model
```{r}
cp_model <- lm(wait ~ length + interest_ya + interest_senior + story + Outdoor, data = data)
summary(cp_model)
anova(cp_model)
```
Interest_senior not sig in sum
Note forward and cp model have same regressors but interest_senior and Outdoor are swapped. 
Same R^2, different ANOVAs


```{r}
com_model <- lm(wait ~ length + interest_ya + Outdoor + story, data = data)
summary(com_model)
anova(com_model)
```
All variables sig in sum and anova


We will continue using the rsq_model because it has the best adjusted R^2 despite the 3 regressors being not sig in summary.

Looking for influence and leverage points:
```{r}
inf_meas <- influence.measures(rsq_model)
true_false <- inf_meas$is.inf
```


Residual Analysis:
```{r}
residuals_rsq <- rstandard(rsq_model)
qqnorm(residuals_rsq)
qqline(residuals_rsq)
```
Upper tail could use some help. Other than that its good. page 138 says positive skewed

```{r}
fitted_rsq <- fitted.values(rsq_model)
ggplot()+
  geom_point(aes(x = fitted_rsq, y = residuals_rsq))
```
Relatively good. Slight negative trend on bottom left hand corner. Potential outliers on far right

Residuals vs Regressors:
Length
```{r}
ggplot()+
  geom_point(aes(x = data$length, y = residuals_rsq))
```
Group/cluster near positive and negative y axis.

Interest_teen
```{r}
ggplot()+
  geom_point(aes(x = data$interest_teen, y = residuals_rsq))
```
Horizontal band of points

Interest_ya
```{r}
ggplot()+
  geom_point(aes(x = data$interest_ya, y = residuals_rsq))
```
Right skewed with one outlier at rating 1

Interest_senior
```{r}
ggplot()+
  geom_point(aes(x = data$interest_senior, y = residuals_rsq))
```
More right skewed with few points on lower end


Thrill
```{r}
ggplot()+
  geom_point(aes(x = data$thrill, y = residuals_rsq))
```
Funnel getting smaller the bigger the thrill

Story
```{r}
ggplot()+
  geom_point(aes(x = data$story, y = residuals_rsq))
```
???

Outdoor
```{r}
ggplot()+
  geom_point(aes(x = data$Outdoor, y = residuals_rsq))
```
???

Partial Regressions:
Note can not perform on categorical/indicator variables
```{r}
mod_wo_length <- lm(wait ~ interest_teen + interest_ya + interest_senior + thrill + story + Outdoor, data = data)
mod_w_length_pred <- lm(length ~ interest_teen + interest_ya + interest_senior + thrill + story + Outdoor, data = data)
ggplot()+
  geom_point(aes(x = mod_w_length_pred$residuals, y = mod_wo_length$residuals))
```
Decent positive correlation


```{r}
mod_wo_int_teen <- lm(wait ~ length + interest_ya + interest_senior + thrill + story + Outdoor, data = data)
mod_w_int_teen_pred <- lm(interest_teen ~ length + interest_ya + interest_senior + thrill + story + Outdoor, data = data)
ggplot()+
  geom_point(aes(x = mod_w_int_teen_pred$residuals, y = mod_wo_int_teen$residuals))
```
Blob, agrees with summary says non sig

```{r}
mod_wo_int_ya <- lm(wait ~ length + interest_teen + interest_senior + thrill + story + Outdoor, data = data)
mod_w_int_ya_pred <- lm(interest_ya ~ length + interest_teen + interest_senior + thrill + story + Outdoor, data = data)
ggplot()+
  geom_point(aes(x = mod_w_int_ya_pred$residuals, y = mod_wo_int_ya$residuals))
```
More blob same as above

```{r}
mod_wo_int_sen <- lm(wait ~ length + interest_teen + interest_ya + thrill + story + Outdoor, data = data)
mod_w_int_sen_pred <- lm(interest_senior ~ length + interest_teen + interest_ya + thrill + story + Outdoor, data = data)
ggplot()+
  geom_point(aes(x = mod_w_int_sen_pred$residuals, y = mod_wo_int_sen$residuals))
```
Want relationship, see none. that is good because agrees with summary saying not sig


```{r}
mod_wo_thrill <- lm(wait ~ length + interest_teen + interest_ya + interest_senior + story + Outdoor, data = data)
mod_w_thrill_pred <- lm(thrill ~ length + interest_teen + interest_ya + interest_senior + story + Outdoor, data = data)
ggplot()+
  geom_point(aes(x = mod_w_thrill_pred$residuals, y = mod_wo_thrill$residuals))
```
Could draw multiple lines thru:/
