---
title: "Ride vs Show"
author: "Pearl Muensterman"
date: "12/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(olsrr)
library(MASS)
```


```{r}
data4 <- read_excel("clean_amusement_data.xlsx")

str(data4)
data4 <- mutate(data4, main = if_else(main == "No", 0, 1))
data4 <- mutate(data4, story = if_else(story == "No", 0, 1))
data4 <- mutate(data4, Indoor = if_else(location == "Indoor", 1, 0),
                     Outdoor = if_else(location == "Outdoor", 1, 0))
data4 <- mutate(data4, interest_adult_avg = (interest_adult + interest_teen + interest_ya)/3)
data4 <- mutate(data4, ride = if_else(vehicle == "Show", 0, 1))
data_ride <- dplyr::select(data4, -location, -name, -vehicle, -interest_adult, -interest_teen, -interest_ya)
```


All Possible
```{r}
park_model <- lm(wait ~ ., data = data_ride)
all_poss_model_4 <- ols_step_all_possible(park_model)
which.max(all_poss_model_4$adjr)
all_poss_model_4[6476,]$adjr
all_poss_model_4[6476,]$predictors
which.min(all_poss_model_4$cp)
all_poss_model_4[470,]$predictors
```
Adjusted R^2: length interest_preschool story thrill Outdoor interest_adult_avg ride
Adjusted R^2 = 0.6141189
Best cp: story Outdoor interest_adult_avg ride


```{r}
full_mod <- lm(wait ~ ., data = data_ride)
base_mod <- lm(wait ~ 1, data = data_ride)
forward_mod <- stepAIC(base_mod, direction = "forward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
forward_mod$anova
```
ride, interest_adult_avg, thrill, sense, story, interest_senior, interest_preschool, length


```{r}
backward_mod <- stepAIC(full_mod, direction = "backward", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
backward_mod$anova
```
length, interest_preschool, interest_senior, story, thrill, sense, interest_adult_avg, ride

```{r}
step_mod <- stepAIC(full_mod, direction = "both", trace = FALSE, 
                       scope = list(upper = full_mod, lower = base_mod))
step_mod$anova
```
length, interest_preschool, interest_senior, story, thrill, sense, interest_adult_avg, ride

```{r}
mod37 <- lm(wait ~ length + interest_preschool + interest_senior + story + thrill + sense + interest_adult_avg + ride, data = data_ride)
summary(mod37)
anova(mod37)
```
Adj R2 0.5845 (best so far)

```{r}
mod37_sig <- lm(wait ~ story + thrill + interest_adult_avg + ride, data = data_ride)
summary(mod37_sig)
```
Adj r2 0.5558

```{r}
mod37_anova <- lm(wait ~ length + interest_preschool + interest_senior + story + sense + interest_adult_avg + ride, data = data_ride)
summary(mod37_anova)
```
Adj R2 0.5666 (better than summary regressors)


RESIDUALS ON THIS MODEL:
wait ~ length + interest_preschool + interest_senior + story + thrill + sense + interest_adult_avg + ride

```{r}
residuals_ride <- rstandard(mod37)
qqnorm(residuals_ride)
qqline(residuals_ride)
```
Upper tail could use some help. Other than that its good. page 138 says positive skewed
Positive skew thought because shows yeah

```{r}
fitted_37 <- fitted.values(mod37)
ggplot()+
  geom_point(aes(x = fitted_37, y = residuals_ride))
```

Transformation probs wont help. Just need more appropriate variables.
